---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Decision Trees :

```{r}
dataset=read.csv("C://Users//Administrator//Desktop//wines_velse1.csv",header=T)
dataset

```

```{r}
dim(dataset)

sample_size=sample.int(n=nrow(dataset),size=floor(0.70*nrow(dataset)),replace = F)
train=dataset[sample_size,]
test=dataset[-sample_size,]

tree_model=rpart(type~.,data=train)


predicted_model=predict(tree_model,newdata=test,type="class")
summary(predicted_model)
confmat=table(predicted_model,test$type)
accuracy=sum(diag(confmat))/sum(confmat)
accuracy

```


### Predictive analysis using regression model :

```{r}
employee=read.csv("C://Users//Administrator//Desktop//regression_data.csv",header=T)
employee


employee$Salary=as.numeric(employee$Salary)
dim(employee)
```



```{r}
sample_size=sample.int(n=nrow(employee),size=floor(0.70*nrow(employee)),replace = F)

train_data=employee[sample_size,]
test_data=employee[-sample_size,]

regression_model=lm(Salary~Exp_year,data=train_data)

summary(regression_model)



```


```{r}
predicted_model_regression=predict(regression_model,newdata = test_data)
predicted_model_regression

```

### plotting the model based on training dataset :

```{r}
library(ggplot2)
library(dplyr)

ggplot() + geom_point(aes(x=train_data$Exp_year,y=train_data$Salary),col="red",size=2) + geom_line(aes(x=train_data$Exp_year,y=predict(regression_model,train_data)),col="blue") + theme_bw()


```

### Ploting regression model based on new data on test dataset:


```{r}

ggplot() + geom_point(aes(x=test_data$Exp_year,y=test_data$Salary),col="red",size=2) + geom_line(aes(x=train_data$Exp_year,y=predict(regression_model,train_data)),col="blue") + theme_bw() + labs(x="Years of Experience",y="Salary",title="Predictive Analysis using Regression Model")

```
### Naive Bayes algorithm applying on weather data and we should justify that whether a boy will play or not : Classification based problem :

```{r}
data=read.csv("C://Users//Administrator//Desktop//weather_data_rf.csv",header=T)
data

sapply(data,class)
dim(data)
```

```{r}
index_no=sample.int(n=nrow(data),size=floor(0.77*nrow(data)),replace = F)
training_data=data[index_no,]
testing_data=data[-index_no,]

library(naivebayes)
training_model=naive_bayes(Play~Temperature+Outlook,training_data)


predicting_model=predict(training_model,newdata = testing_data)


confmat=table(predicting_model,testing_data$Play)
confmat

accuracy=sum(diag(confmat))*100/sum(confmat)
accuracy
```

### Naive Bayes : 
```{r}
purchase_data=read.csv("C://Users//Administrator//Desktop//Social_Network_Ads.csv",header = T)
purchase_data=purchase_data[,3:5]
purchase_data$Purchased=as.factor(purchase_data$Purchased)
purchase_data



```


```{r}
sample_data=sample.int(n=nrow(purchase_data),size=floor(0.75*nrow(purchase_data)),replace=F)
train_data=purchase_data[sample_data,]
test_data=purchase_data[-sample_data,]

train_data[-3]=scale(train_data[-3])
test_data[-3]=scale(test_data[-3])

naive_model=naive_bayes(Purchased~EstimatedSalary,train_data)

predicting_model=predict(naive_model,newdata=test_data)

predicting_model

confusion_matrix=table(predicting_model,test_data$Purchased)
accuracy=sum(diag(confusion_matrix))*100/sum(confusion_matrix)
accuracy

```

### Multiple Linear Regression Model:

```{r}
dataset=read.csv("C://Users//Administrator//Desktop//50_Startup.csv",header = T)
dataset


```


```{r}
dim(dataset)
sapply(dataset,class)
colSums(!is.na(dataset))*100/nrow(dataset)
dataset=dataset[,-4]
dataset


```

```{r}

sample_size=sample.int(n=nrow(dataset),size=floor(0.80*nrow(dataset)),replace = F)



train_model=dataset[sample_size,]
test_model=dataset[-sample_size,]



regression_model=lm(formula=Profit ~ .,data=train_model)
summary(regression_model)
predicted_model_regression=predict(regression_model,newdata=test_model)
predicted_model_regression




```
### Here the invester should invest on the 5th company to make more profit.........................   







### Logistic Regression Predictive model :

```{r}
logis=read.csv("C://Users//Administrator//Desktop//Social_Network_Ads.csv",header = T)
logis
dim(logis)
str(logis)
```


```{r}
sample_size=sample.int(n=nrow(logis),size=floor(0.75*nrow(logis)),replace = F)
train_data=logis[sample_size,]
test_data=logis[-sample_size,]

train_data[-3]=scale(train_data[-3])
test_data[-3]=scale(test_data[-3])



training_data_model= glm(Purchased~.,family = binomial,data=train_data)

predicted_model=predict(training_data_model,type='response',newdata=test_data[-3])
new_pred_modell=if_else(predicted_model>=0.5,1,0)

new_pred_modell



```


```{r}
library(ElemStatLearn)

set = test_data

X1 = seq(min(set[, 1]) - 1, max(set[, 1]) + 1, by = 0.01)
X2 = seq(min(set[, 2]) - 1, max(set[, 2]) + 1, by = 0.01)

grid_set = expand.grid(X1, X2)
colnames(grid_set) = c('Age', 'EstimatedSalary')
prob_set = predict(training_data_model, type = 'response', newdata = grid_set)
y_grid = ifelse(prob_set > 0.5, 1, 0)
plot(set[, -3],
     main = 'Logistic Regression Model',
     xlab = 'Age', ylab = ' Salary',
     xlim = range(X1), ylim = range(X2))
contour(X1, X2, matrix(as.numeric(y_grid), length(X1), length(X2)), add = TRUE)
points(grid_set, pch = '.', col = ifelse(y_grid == 1, 'springgreen3', 'tomato'))
points(set, pch = 21, bg = ifelse(set[, 3] == 1, 'green4', 'red3'))

````
### Weather a boy will play or not - Prediction by using naive bayes classification

```{r}
data2=read.csv("C://Users//Administrator//Desktop//weather_data_rf.csv")




sample_size=sample.int(n=nrow(data2),size=floor(0.75*nrow(data2)),replace=F)


 train_data=data2[sample_size,]
test_data=data2[-sample_size,]

train_data_model=naive_bayes(Play~Wind+Outlook+Temperature, data=train_data)


predicted_model=predict(train_data_model,newdata=test_data)






cm=table(test_data$Play,predicted_model)

accuracy=sum(diag(cm))*100/sum(cm)
accuracy

```
### Prediction of petrol Price in future : From Jan 2015-June 2017

```{r}
petrol=read.csv("C://Users//Administrator//Desktop//petrol_Price.csv",header = T)
petrol
sapply(petrol,class)

cor(petrol)
```

```{r}
sample_size=sample.int(n=nrow(petrol),size=floor(0.7*nrow(petrol)),replace=F)
sample_size

train_data=petrol[sample_size,]
test_data=petrol[-sample_size,]

model=lm(Petrol.Price~.,data=train_data)

prediction=predict(model,newdata = test_data)
prediction


```


```{r}
ggplot() + geom_point(aes(x=test_data$Month,y=test_data$Petrol.Price,group=1),col="red") + geom_line(aes(x=train_data$Month,y=predict(model,newdata=train_data),group=1),col="blue") 



```


